Cross Validation Approaches for Penalized Cox Regression

### 2022-08-10 sub/smimr/1/cover.tex
SMM: Referee comments

\StartLetter{}{Dear editors of {\em Statistics in Medicine},}

We are submitting the manuscript ``Cross validation approaches for penalized Cox regression'' for your consideration to be published in {\em Statistics in Medicine}.

Using cross-validation (CV) for model selection is fairly straightforward in most models.  However, for models based on partial likelihood, such as Cox regression, we obtain predictions only of relative risk, not absolute risk, thereby complicating the cross-validation paradigm.  This work proposes a new approach for CV in these models and demonstrates that it achieves a combination of performance and stability that existing methods do not match.  We believe this is an accessible article of clear practical importance, and would be interesting to readers of {\em Statistics in Medicine}.

>>>>

\StartLetter{}{Dear editors of {\em Statistical Methods in Medical Research},}

We are submitting the manuscript ``Cross validation approaches for penalized Cox regression'' for your consideration to be published in {\em Statistical Methods in Medical Research}.

Using cross-validation (CV) for model selection is fairly straightforward in most models.  However, for models based on partial likelihood, such as Cox regression, we obtain predictions only of relative risk, not absolute risk, thereby complicating the cross-validation paradigm.  This work proposes a new approach for CV in these models and demonstrates that it achieves a combination of performance and stability that existing methods do not match.  We believe this is an accessible article of clear practical importance, and would be interesting to readers of {\em Statistical Methods in Medical Research}.
